### 2018-04-09 latex/icpp18/experiments.tex
removed k=16 for all experiments

%%%%%%%%%%% Strong scaling flickr %%%%%%%%
\begin{figure}
\begin{subfigure}[t]{0.5\textwidth}
\begin{tikzpicture}
\renewcommand{\minvalue}{291.82}
\renewcommand{\numiterations}{30}
\renewcommand{\datafile}{data/flickr-speedup16.dat}
\speedup
\end{tikzpicture}
\subcaption{Flickr dataset with low rank $k=16$ on Rhea}
\label{fig:flickr-speedup-16}
\end{subfigure}

@@

\begin{figure}
\begin{subfigure}[t]{0.5\textwidth}
\begin{tikzpicture}
\renewcommand{\minvalue}{400.8}
\renewcommand{\datafile}{data/delicious-speedup16.dat}
\speedup
\end{tikzpicture}
\subcaption{Delicious dataset with low rank $k=16$ on Rhea}
\label{fig:delicious-speedup-16}
\end{subfigure}

@@

%\begin{subfigure}[t]{0.5\textwidth}
%\begin{tikzpicture}
%\bgqtrue
%\renewcommand{\minvalue}{186.1}
%\renewcommand{\numiterations}{10}
%\renewcommand{\datafile}{data/delicious-speedup-bgq.dat}
%\speedup
%\end{tikzpicture}
%\subcaption{Flickr dataset Low Rank $k=48$ on Bluegene/Q}
%\end{subfigure}
%

\begin{subfigure}[t]{0.5\textwidth}
\begin{tikzpicture}
\bgqtrue
\renewcommand{\minvalue}{186.1}
\renewcommand{\numiterations}{10}
\renewcommand{\datafile}{data/delicious-speedup-bgq.dat}
\speedup
\end{tikzpicture}
\subcaption{Delicious dataset low rank $k=48$ on Bluegene/Q}
\label{fig:delicious-speedup-bgq}
\end{subfigure}

@@

\renewcommand{\minvalue}{1}
\begin{figure}
\begin{subfigure}[t]{0.25\textwidth}
\begin{tikzpicture}
\ylabeltrue
\legendfalse
\renewcommand{\numiterations}{30}
\renewcommand{\datafile}{data/flickr-details16-16.dat}
\makeplot
\end{tikzpicture}
\subcaption{Rhea $p=16$, Low Rank $k=16$}
\end{subfigure}
~
\begin{subfigure}[t]{0.25\textwidth}
\begin{tikzpicture}
\ylabelfalse
\legendtrue
\renewcommand{\numiterations}{30}
\renewcommand{\datafile}{data/flickr-details3072-16.dat}
\makeplot
\end{tikzpicture}
\subcaption{Rhea $p=3072$, Low Rank $k=16$}
\end{subfigure}

@@

@@

\renewcommand{\minvalue}{1}
\begin{figure}
\begin{subfigure}[t]{0.25\textwidth}
\begin{tikzpicture}
\ylabeltrue
\legendfalse
\renewcommand{\numiterations}{30}
\renewcommand{\datafile}{data/delicious-details16-16.dat}
\makeplot
\end{tikzpicture}
\subcaption{Rhea $p=16$, Low rank $k=16$}
\end{subfigure}
~
\begin{subfigure}[t]{0.25\textwidth}
\begin{tikzpicture}
\ylabelfalse
\legendtrue
\renewcommand{\numiterations}{30}
\renewcommand{\datafile}{data/delicious-details3072-16.dat}
\makeplot
\end{tikzpicture}
\subcaption{Rhea $p=3072$, Low rank $k=16$}
\end{subfigure}

>>>>

%%%%%%%%%%% NNZ Sweep %%%%%%%%

\begin{figure}
\renewcommand{\numiterations}{30}
\renewcommand{\minvalue}{1}
\begin{subfigure}[t]{0.5\textwidth}
\begin{tikzpicture}
\begin{axis}[xlabel=Edge Factor, ylabel=Time(in Secs),width=3.5in, height=2.0in, 
y label style={yshift=-.5cm}, 
%legend pos=outer, legend style={draw=none,row sep=-0.1cm},
%legend style={draw=none,at={(0.5,-0.1)},anchor=north},
%legend columns = -1,
%legend pos=outer north west, legend style={draw=none,row sep=-0.1cm},
xtick=data, 
xticklabels={4, 8, 16, 32, 64}
]
\addplot  table [x={edgefactor}, y expr=(\thisrow{collective}/(\minvalue*\numiterations))] {data/nnzsweepall_k48_p4096_comp.dat};
\addplot  table [x={edgefactor}, y expr=(\thisrow{cp1d}/(\minvalue*\numiterations))] {data/nnzsweepall_k48_p4096_comp.dat};
\addplot  table [x={edgefactor}, y expr=(\thisrow{cp2d}/(\minvalue*\numiterations))] {data/nnzsweepall_k48_p4096_comp.dat};
\addplot  table [x={edgefactor}, y expr=(\thisrow{cr}/(\minvalue*\numiterations))] {data/nnzsweepall_k48_p4096_comp.dat};
\addplot  table [x={edgefactor}, y expr=(\thisrow{cu}/(\minvalue*\numiterations))] {data/nnzsweepall_k48_p4096_comp.dat};
%\legend{collective, cp1d, cp2d, cr, cu}
\end{axis}
\end{tikzpicture}
\subcaption{Computation cost for low rank $k$=48 on 4096 procs}
\label{fig:nnzsweepcomp}
\end{subfigure}

\begin{subfigure}[t]{0.5\textwidth}
\begin{tikzpicture}
\begin{axis}[xlabel=Edge Factor, ylabel=Time(in Secs),width=3.5in, height=2.0in, 
y label style={yshift=-.5cm}, 
%legend pos=outer north west, legend style={draw=none,row sep=-0.1cm},
xtick=data, 
xticklabels={4, 8, 16, 32, 64},
legend style={draw=none,at={(0.5,-0.3)},anchor=north},
legend columns = -1
]

\addplot  table [x={edgefactor}, y expr=(\thisrow{collective}/(\minvalue*\numiterations))] {data/nnzsweepall_k48_p4096_comm.dat};
\addplot  table [x={edgefactor}, y expr=(\thisrow{cp1d}/(\minvalue*\numiterations))] {data/nnzsweepall_k48_p4096_comm.dat};
\addplot  table [x={edgefactor}, y expr=(\thisrow{cp2d}/(\minvalue*\numiterations))] {data/nnzsweepall_k48_p4096_comm.dat};
\addplot  table [x={edgefactor}, y expr=(\thisrow{cr}/(\minvalue*\numiterations))] {data/nnzsweepall_k48_p4096_comm.dat};
\addplot  table [x={edgefactor}, y expr=(\thisrow{cu}/(\minvalue*\numiterations))] {data/nnzsweepall_k48_p4096_comm.dat};\legend{collective, cp1d, cp2d, cr, cu}
\end{axis}
\end{tikzpicture}
\subcaption{Communication cost for low rank $k$=48 on 4096 procs}
\label{fig:nnzsweepcomm}
\end{subfigure}

\end{figure}

%%%%%%%%%%% Strong scaling flickr %%%%%%%%
\begin{figure}
%\begin{subfigure}[t]{0.5\textwidth}
%\begin{tikzpicture}
%\renewcommand{\minvalue}{291.82}
%\renewcommand{\numiterations}{30}
%\renewcommand{\datafile}{data/flickr-speedup16.dat}
%\speedup
%\end{tikzpicture}
%\subcaption{Flickr dataset with low rank $k=16$ on Rhea}
%\label{fig:flickr-speedup-16}
%\end{subfigure}

@@

\begin{figure}
%\begin{subfigure}[t]{0.5\textwidth}
%\begin{tikzpicture}
%\renewcommand{\minvalue}{400.8}
%\renewcommand{\datafile}{data/delicious-speedup16.dat}
%\speedup
%\end{tikzpicture}
%\subcaption{Delicious dataset with low rank $k=16$ on Rhea}
%\label{fig:delicious-speedup-16}
%\end{subfigure}

@@

%\begin{subfigure}[t]{0.5\textwidth}
%\begin{tikzpicture}
%\bgqtrue
%\renewcommand{\minvalue}{186.1}
%\renewcommand{\numiterations}{10}
%\renewcommand{\datafile}{data/delicious-speedup-bgq.dat}
%\speedup
%\end{tikzpicture}
%\subcaption{Flickr dataset Low Rank $k=48$ on Bluegene/Q}
%\end{subfigure}
%
~
\begin{subfigure}[t]{0.5\textwidth}
\begin{tikzpicture}
\bgqtrue
\renewcommand{\minvalue}{186.1}
\renewcommand{\numiterations}{10}
\renewcommand{\datafile}{data/delicious-speedup-bgq.dat}
\speedup
\end{tikzpicture}
\subcaption{Delicious dataset low rank $k=48$ on Bluegene/Q}
\label{fig:delicious-speedup-bgq}
\end{subfigure}

@@

\renewcommand{\minvalue}{1}
\begin{figure}

%\begin{subfigure}[t]{0.25\textwidth}
%\begin{tikzpicture}
%\ylabeltrue
%\legendfalse
%\renewcommand{\numiterations}{30}
%\renewcommand{\datafile}{data/flickr-details16-16.dat}
%\makeplot
%\end{tikzpicture}
%\subcaption{Rhea $p=16$, Low Rank $k=16$}
%\end{subfigure}
%~
%\begin{subfigure}[t]{0.25\textwidth}
%\begin{tikzpicture}
%\ylabelfalse
%\legendtrue
%\renewcommand{\numiterations}{30}
%\renewcommand{\datafile}{data/flickr-details3072-16.dat}
%\makeplot
%\end{tikzpicture}
%\subcaption{Rhea $p=3072$, Low Rank $k=16$}
%\end{subfigure}

@@

%%%%%%%%%%% Stackexchange Details %%%%%%%%
%\renewcommand{\minvalue}{1}
\begin{figure}

%\begin{subfigure}[t]{0.25\textwidth}
%\begin{tikzpicture}
%\ylabelfalse
%\legendtrue
%\renewcommand{\numiterations}{30}
%\renewcommand{\datafile}{data/stkx-details1536-16.dat}
%\makeplot
%\end{tikzpicture}
%\subcaption{Rhea $p=1536$, Low Rank $k=16$}
%\end{subfigure}

\begin{subfigure}[t]{0.25\textwidth}
\begin{tikzpicture}
\ylabelfalse
\legendtrue
\renewcommand{\numiterations}{30}
\renewcommand{\datafile}{data/stkx-details1536-48.dat}
\makeplot
\end{tikzpicture}
\subcaption{Rhea $p=1536$, Low Rank $k=48$}
\end{subfigure}

\begin{subfigure}[t]{0.5\textwidth}
\begin{tikzpicture}
\bgqtrue
\renewcommand{\minvalue}{137.1}
\renewcommand{\numiterations}{10}
\renewcommand{\datafile}{data/stackoverflow-speedup-bgq.dat}
\speedup
\end{tikzpicture}
\subcaption{Stackoverflow dataset Low Rank $k=48$ on Bluegene/Q}
\end{subfigure}

\caption{Stack exchange dataset Time Split up for Low Rank $k=16, 48$ on Rhea and Strong scaling on Bluegene/Q}
\label{fig:flickrdetails}
\end{figure}

@@

%\renewcommand{\minvalue}{1}
\begin{figure}

%\begin{subfigure}[t]{0.25\textwidth}
%\begin{tikzpicture}
%\ylabeltrue
%\legendfalse
%\renewcommand{\numiterations}{30}
%\renewcommand{\datafile}{data/delicious-details16-16.dat}
%\makeplot
%\end{tikzpicture}
%\subcaption{Rhea $p=16$, Low rank $k=16$}
%\end{subfigure}
%~
%\begin{subfigure}[t]{0.25\textwidth}
%\begin{tikzpicture}
%\ylabelfalse
%\legendtrue
%\renewcommand{\numiterations}{30}
%\renewcommand{\datafile}{data/delicious-details3072-16.dat}
%\makeplot
%\end{tikzpicture}
%\subcaption{Rhea $p=3072$, Low rank $k=16$}
%\end{subfigure}
